Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}

### 2023-02-24 nakayama/images/algebraic-structures.tex
Converted to use Springer Nature document class

\tikzset{
    node/.style = {
       shape=rectangle, %rounded corners,
       align=center,
       minimum width = .4cm,
       minimum height = .4cm,
 %      fill = gray!30
 %      fill = cyan!40
 %      fill = blue!50!white!80
    },
    Snode/.style = {
       shape=rectangle, %rounded corners,
       align=center,
       minimum width = .4cm,
       minimum height = .4cm,
       fill = green!60!blue!70
    }
%    bad/.style = {
%       shape=rectangle, %rounded corners,
%       align=center,
%       minimum width = .4cm,
%       minimum height = .4cm,
%       fill = red!70
%    }
}
\begin{document}

>>>>

\tikzset{
    node/.style = {
       shape=rectangle, %rounded corners,
       align=center,
       minimum width = .4cm,
       minimum height = .4cm,
    },
    Snode/.style = {
       shape=rectangle, %rounded corners,
       align=center,
       minimum width = .4cm,
       minimum height = .4cm,
       fill = green!60!blue!70
    }
}
\begin{document}

### 2023-02-24 nakayama/paper.tex
Converted to use Springer Nature document class

\RequirePackage[l2tabu,orthodox]{nag}
\documentclass{article}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{minted}

\input{preamble.tex}

\begin{document}
\title{ 
Formalizing Commutative Algebra in Coq: \\
Nakayama's Lemma\thanks{Source code for this work is available on the following
site: \url{https://github.com/ku-sldg/algebra}}
}

\date{}

\author{ 
	Andrew Cousino \\ {\ttfamily acousino@ku.edu}
	\and 
	Emily E.\ Witt\thanks{Witt acknowledges support from NSF CAREER Award
    DMS-1945611, the Keeler Intra-University Professorship from the University of Kansas, and the Ruth I.\, Michler Memorial Prize from the
    Association for Women in Mathematics.} \\ {\ttfamily witt@ku.edu}
  \and 
	Perry Alexander \\ {\ttfamily palexand@ku.edu}
}

@@

\vspace{-1cm}

{\large
\begin{center}
	Institute for Information Sciences \\
	The University of Kansas \\
	Lawrence, KS 66045
\end{center}
}

\todo[inline]{To do:  Add to/alter author list, funding acknowledgments, title,
  and/or abstract as needed}

\begin{abstract}
  We describe our formal proof of Nakayama's Lemma, a fundamental theorem in
  the mathematical field of commutative algebra. The statement and proof of
  this result involve several commutative-algebraic structures including
  commutative rings, ideals of these rings, and modules over them, and we also
  explain our process of formalizing these structures.
\end{abstract}

\noindent \textbf{Keywords:}
formalization of mathematics,
formal proof,
commutative algebra,
commutative ring,
local ring,
ideal,
module over a ring,
finitely generated module.

@@

Commutative algebra also has broad applications to science and technology. For
instance, it has been integral to advances in robotics \cite{cox-little-oshea},
and has helped form our current understanding of the human genome
\cite{genetic-algebra}. The commutative-algebraic notion of a Gr\"{o}bner
basis, a special type of generating set for an ideal in a ring of polynomials,
has become a fundamental computational tool in coding theory and cryptography
(e.g., see  \cite{grobner-bases-cryptography}). A implementation of
Buchberger's algorithm \cite{buchberger} for determining Gr\"obner bases of
ideals in polynomial rings has been proved correct within the proof assistant
Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an
integrated formal development of the algorithm in Coq has also been carried out
\cite{persson2001integrated} (see also \cite{grobner-type-theory}).

Our goal is to newly formalize theoretical, rather than computational,
commutative algebra in Coq. We formally prove \emph{Nakayama's Lemma}
\cite{nakayama-1951, azumaya}, an essential result in the field. In doing so,
we formalize algebraic structures that are fundamental to higher-level algebra,
such as \emph{local rings} and \emph{modules over commutative rings}, and
\emph{quotient rings and modules}. Rather than build upon some of the basic
objects from abstract algebra, such as groups and rings, that have been
formalized in Coq, e.g., in the \emph{Mathematical Components Library}
\cite{mathcomp}, we start from scratch.
\todo{To do: Verify whether MathComp only formalized finite algebraic
  structures. Drew is about as certain as he can be that this is the case.}
The theory, including the formalization of all algebraic structures, makes up
approximately $100$ kB, and 3300 lines of code.

@@

\begin{figure}[t]
  \caption{The hierarchy of our algebraic structures in Coq}
  \includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
  \centering
   \label{alg-heirarchy: F}
\end{figure}

@@

%\emily[inline]{Emily:  Unfortunately, I think we need to update naming
%  conventions since in mathematics, ``vector'' is reserved for an element of a
%  vector space over a field, rather than an element of an arbitrary module.  So
%  this could cause confusion.  Similar with ``basis,'' which is especially
%  tricking since two different generating sets of a finitely generated module
%  can have different sizes, but all bases of a vector space have the same
%  cardinality, and an element of a module can typically be written as a scalar
%  combination in multiple ways, while bases are linearly independent.  I've
%  proposed a rewrite of the blue subsubsection right above it.  Drew, can you
%  double check it for accuracy with respect to the code? 
%}
%\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
%  should be something like {\ttfamily scalar-combinations}, and
%  {\ttfamily basis} something like {\ttfamily generating-set}. 
%}

@@

\begin{minted}{coq}
  Definition finitely_generated {n: nat}(generatingSet: t M n) :=
    forall (elt: M),
      exists (coeffs: t R n),
        elt =M= linear_combin coeffs generatingSet.
\end{minted}

@@

\emily[inline]{Emily says:  There was an issue with our argument below, so I have updated it, and need to point to 
quotients to deal with the fact that we want a maximal ideal \emph{that contains a fixed element}.
}

@@

Even if it were possible not to overwhelm a system with
these infinitely many calls to a single proof tactic, one would still have to
invoke more tactics to finish the proof with an application of Zorn's lemma,
which finally guarantees us a maximal ideal containing \(x\). To summarize, we
are forced to run the following proof script which will never get past calling
\mintinline{coq}{generate_larger_ideal} infinitely many times.
\begin{minted}{coq}
  repeat generate_larger_ideal. (* must be called infinitely often *)
  zorns_lemma. (* called after the above non-terminating call finishes *)
\end{minted}

@@

\begin{minted}{coq}
Axiom comm_ring_nonunit_maximal_ideal:
  forall (x: Carrier),
    ~ is_unit equiv mul one x ->
    exists (P: Carrier -> Prop)(P_proper: Proper (equiv ==> iff) P)
    	(P_ideal: Ideal add zero minus mul P),
      P x /\ maximal_ideal P.
\end{minted}

@@

\begin{minted}{coq}
Context {P_ideal: Ideal Radd Rzero Rminus Rmul P}.
Context {P_maxideal: maximal_ideal Requiv Radd Rzero Rminus Rmul P}.
Context {R_local: local_ring Requiv Radd Rzero Rminus Rmul}.

@@

\begin{minted}{coq}
Lemma module_fin_gen_ideal_module:
  forall {n: nat}(generatingSet: t M n),
    finitely_generated Mequiv Madd Mzero action generatingSet ->
    forall {m: nat}(coeffs: t R m)(elts: t M m),
      Forall P coeffs ->
      exists (coeffs': t R n),
        linear_combin Madd Mzero action coeffs elts =M=
          linear_combin Madd Mzero action coeffs' generatingSet /\
        Forall P coeffs'.
\end{minted}

This lemma's proof follows from a straightforward argument based on definitions, by
induction on the number of elements in a fixed generating set for $M$, which we
informally describe: By definition, $x \in I M$ can  be written, for some
positive integer $k$ and elements $r_i \in R$ and $w_i \in M$,
$1 \leq i \leq k$, as $x = r_1 \cdot w_1 + r_2 \cdot w_2 + \cdots +
r_k \cdot w_k$. What's more, by definition of a finite generating set $u_{1},
\dots, u_{n}$ for $M$, each $w_i$ equals $c_{i1} \cdot u_1 + c_{i2} \cdot u_2 +
\cdots + c_{in} \cdot u_n$ for appropriate choices of $c_{ij} \in R$. Hence,
inductively applying associativity, 
\begin{align*}
  x = \sum_{i=1}^{k} r_i \cdot w_i
    = \sum_{i=1}^{k} r_i \cdot \left(\sum_{j=1}^n c_{ij} \cdot  u_j\right)
    = \sum_{j=1}^{n}\sum_{i=1}^{k} r_i \cdot (c_{ij} \cdot u_j) 
    = \sum_{j=1}^{n}\left(\sum_{i=1}^{k} c_{ij} \cdot r_i\right) \cdot u_j.   
\end{align*}
By the absorption property of ideals, each  $c_{ij}  \cdot r_i$ is in $I$, and since ideals
are closed under addition, we inductively conclude that the coefficient $a_j
:= c_{1j} \cdot  r_1 +  c_{2j} \cdot  r_2 +  \cdots c_{kj}\cdot r_k$ of $u_j$
is also in $I$.

@@

In Coq, we work backward to establish \eqref{equation1: e}. The comment following
each tactic appearing in the code below offers a brief indication of its effects on the goal.
\begin{minted}[linenos,firstnumber=157,stepnumber=5]{coq}
  assert ((Rone [+] Rminus a1) <.> u1 =M= (* (1 - a1) u1 = ... *)
    linear_combin Madd Mzero action coeffs' generatingSet').
  { setoid_rewrite (module_distrib_Radd Radd Rmul Rone
      Mequiv Madd Mzero Mminus action). (* 1 u1 + (-a1) u1 = ... *)
    setoid_rewrite (module_Rone Radd Rmul Rone
      Mequiv Madd Mzero Mminus action). (* u1 + (-a1) u1 = ... *)
    setoid_rewrite (module_minus_l Requiv Radd Rzero Rminus Rmul Rone
      Mequiv Madd Mzero Mminus action). (* u1 - a1 u1 = ... *)
    symmetry. (* ... = u1 - a1 u1 *)
    apply (group_move_r Mequiv Madd Mzero Mminus). (* ... + a1 u1 = u1 *)
    symmetry. (* u1 = ... + a1 u1 *)
    assumption. }
\end{minted}

Since a proper ideal contains no units and $a_1$ is taken to be in
$\mathfrak{m}$, it is not a unit. Hence, by the formalized statement mentioned
early in \Cref{formal-proof: S}, $1 - a_{1}$ is a unit of $R$. Let $b_{1} \in R$ denote its 
multiplicative inverse, so that $b_1 \cdot  (1 - a_{1}) = 1$. Multiplying this
element on the either side of \eqref{equation1: e}, we deduce the following.  
\begin{align}
\label{simplify-line-1}
b_1 \cdot \left((1 - a_{1}) \cdot u_{1} \right)
  & = b_1 \cdot (a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1}) \\ 
\label{simplify-line-2}
\left( b_1 \cdot (1 - a_{1})\right) \cdot u_{1}
  & = b_1 \cdot (a_{2} \cdot u_{2}) + \cdots + b_1 \cdot (a_{n+1} \cdot u_{n+1}) \\ 
   \label{simplify-line-3}
u_1 = 1 \cdot u_{1}
  & = (b_1 \cdot  a_{2}) \cdot u_{2} + \cdots + (b_1  \cdot  a_{n+1}) \cdot u_{n+1} 
\end{align}
\begin{minted}[linenos,firstnumber=181,stepnumber=5]{coq}
  pose proof
    (local_comm_ring_sub_1_nonunit Requiv Radd Rzero Rminus Rmul Rone
      R_local x1 Hx1_nonunit) as H1ma1_unit.
  (* Getting to u1 = (b1 coeffs') . generatingSet *)
  inversion_clear H1ma1_unit as [b1 Hb1]. (* 1 - a1 is a unit *)
  setoid_rewrite (commutative Requiv Rmul) in Hb1. (* b1 (1 - a1) = 1 *)
\end{minted}

This block of code has the effect of naming \(b_{1}\) as the inverse of the
unit \(1 - a_{1}\), and storing in the hypothesis \texttt{Hb1} the equation
\(b_{1} \cdot (1 - a_{1}) = 1\). The remainder of the code goes on to multiply on the
left by \(b_{1}\) in the equation \texttt{H} in order to establish  \eqref{simplify-line-1}.
Going on and applying the axioms of a module over a commutative ring, along with hypothesis \texttt{Hb1}, we can
simplify the left hand side of \texttt{H} to be just \(u_{1}\), as in \eqref{simplify-line-3}.
\begin{minted}[linenos,firstnumber=last,stepnumber=5]{coq}
  apply (module_op_l Requiv Mequiv action) with (r:=b1) in H.
  setoid_rewrite <- (module_distrib_Rmul Radd Rmul Rone
    Mequiv Madd Mzero Mminus action) in H. (* H: (b1 (1 - a1)) u1 = ... *)
  setoid_rewrite Hb1 in H. (* H: (1) u1 = ... *)
  setoid_rewrite (module_Rone Radd Rmul Rone
    Mequiv Madd Mzero Mminus action) in H. (* H: u1 = ... *)
\end{minted}
In particular, the generator $u_1$ can be written as a scalar combination of
the $n$ generators $u_2, \ldots, u_{n+1}$, and is superfluous. Hence $M$ can be
generated by $n$ elements, and $M=0$ by the inductive hypothesis. 
Though showing that the inductive hypothesis holds is more technical in Coq than in this
informal proof, the extra steps are essentially bookkeeping.

@@

\bibliographystyle{plain}
\bibliography{references}
\end{document}

>>>>

\RequirePackage[l2tabu,orthodox]{nag}
\RequirePackage{tikz}
\documentclass[referee,sn-mathphys]{sn-jnl}
% \usepackage{amsthm}
% \usepackage{amssymb}
% \usepackage{mathtools}
\usepackage{minted}
% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{color}
% \usepackage{mathrsfs}
% \usepackage[mathcal]{euscript}
% \usepackage{enumitem}
% \usepackage{float}
% \usepackage[center]{caption}
% \usepackage{graphicx}
\usepackage{cleveref}

\jyear{2021}

% TikZ libraries and settings
\usetikzlibrary{positioning}
\tikzset{
  node/.style = {
    shape=rectangle, %rounded corners,
    align=center,
    minimum width = .4cm,
    minimum height = .4cm,
  },
  Snode/.style = {
    shape=rectangle, %rounded corners,
    align=center,
    minimum width = .4cm,
    minimum height = .4cm,
    fill = green!60!blue!70
  }
}

% Clever references
\crefname{equation}{Eq.}{Eqs.}
\crefname{theorem}{Theorem}{Theorems}
\crefname{lemma}{Lemma}{Lemmata}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{proposition}{Proposition}{Propositions}
\crefname{definition}{Definition}{Definitions}
\crefname{rem}{Remark}{Remarks}
\crefname{example}{Example}{Examples}
\crefname{conventions}{Conventions}{Conventions}
\crefname{setup}{Setup}{Setup}
\crefname{question}{Question}{Question}
\crefname{figure}{Figure}{Figures}

%THEOREM ENVIRONMENTS
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\newtheorem*{nak*}{Nakayama's Lemma}

%DEFINITION STYLE ENVIRONMENTS
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{definition-theorem}[theorem]{Definition/Theorem}
\newtheorem{setup}[theorem]{Setup}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{conventions}[theorem]{Conventions}
\newtheorem{example}[theorem]{Example}

%REMARK STYLE ENVIRONMENTS 
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{convention}{Convention}

\numberwithin{equation}{section}
\numberwithin{figure}{subsection}

%%%%%%%%
% \mathchardef\ordinarycolon\mathcode`\:
% \mathcode`\:=\string"8000
% \begingroup \catcode`\:=\active
%   \gdef:{\mathrel{\mathop\ordinarycolon}}
% \endgroup

\begin{document}
\title[Formalizing Commutative Algebra in Coq]{ 
Formalizing Commutative Algebra in Coq: \\
Nakayama's Lemma\thanks{Source code for this work is available on the following
site: \url{https://github.com/ku-sldg/algebra}}
}

\author[1]{\fnm{Andrew} \sur{Cousino}}\email{acousino@ku.edu}
\author[1]{\fnm{Emily E.\ Witt}}\email{witt@ku.edu}
\author[1]{\fnm{Perry} \sur{Alexander}}\email{palexand@ku.edu}
\affil[1]{\orgdiv{Institute for Information Sciences},
  \orgname{University of Kansas},
  \orgaddress{\city{Lawrence}, \postcode{66045}, \state{Kansas},
    \country{United States of America}}}

\abstract{
  We describe our formal proof of Nakayama's Lemma, a fundamental theorem in
  the mathematical field of commutative algebra. The statement and proof of
  this result involve several commutative-algebraic structures including
  commutative rings, ideals of these rings, and modules over them, and we also
  explain our process of formalizing these structures.
}

\keywords{formalization of mathematics, formal proof, commutative algebra,
  commutative ring, local ring, ideal, module over a ring,
  finitely generated module}

@@

@@

Commutative algebra also has broad applications to science and technology. For
instance, it has been integral to advances in robotics \cite{cox-little-oshea},
and has helped form our current understanding of the human genome
\cite{genetic-algebra}. The commutative-algebraic notion of a Gr\"{o}bner
basis, a special type of generating set for an ideal in a ring of polynomials,
has become a fundamental computational tool in coding theory and cryptography
(e.g., see  \cite{grobner-bases-cryptography}). A implementation of
Buchberger's algorithm \cite{buchberger} for determining Gr\"{o}bner bases of
ideals in polynomial rings has been proved correct within the proof assistant
Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an
integrated formal development of the algorithm in Coq has also been carried out
\cite{persson2001integrated} (see also \cite{grobner-type-theory}).

Our goal is to newly formalize theoretical, rather than computational,
commutative algebra in Coq. We formally prove \emph{Nakayama's Lemma}
\cite{nakayama-1951, azumaya}, an essential result in the field. In doing so,
we formalize algebraic structures that are fundamental to higher-level algebra,
such as \emph{local rings} and \emph{modules over commutative rings}, and
\emph{quotient rings and modules}. Rather than build upon some of the basic
objects from abstract algebra, such as groups and rings, that have been
formalized in Coq, e.g., in the \emph{Mathematical Components Library}
\cite{mathcomp}, we start from scratch.
The theory, including the formalization of all algebraic structures, makes up
approximately $100$ kB, and 3300 lines of code.

@@

\begin{figure}[t]
  \caption{The hierarchy of our algebraic structures in Coq}
  \resizebox{0.5\textwidth}{0.4\textwidth}{
    \begin{tikzpicture}[->,>=stealth,shorten >=1pt,auto,node distance=1cm,semithick]
      \node[Snode] (Semigroup) {Semigroup};
      \node[Snode] (Monoid) [below = of Semigroup]{Monoid};
      \node[Snode] (Group) [below =of Monoid] {Group};
      \node[Snode] (AbelianGroup) [below =of Group] {AbelianGroup};
      \node[Snode] (Subgroup) [left =1.3cm of AbelianGroup] {Subgroup};

      \node[Snode] (Ring) [below = of AbelianGroup] {Ring};
      \node[Snode] (CommutativeRing) [below =of Ring] {CommRing};
      \node[Snode] (Module) [right = 1.3cm of CommutativeRing] {Module};
      \node[Snode] (Submodule) [left = 1.0 of CommutativeRing] {Submodule};
      \node[Snode] (Ideal) [left =1.0 of Submodule] {Ideal};
      \path (Semigroup) edge (Monoid)
        (Monoid) edge (Group)
        (Group) edge (AbelianGroup)
        (Group) edge (Subgroup)
        (Subgroup) edge (Ideal)
        (AbelianGroup) edge (Ring)
        (AbelianGroup) edge (Module)
        (Ring) edge (CommutativeRing)
        (Subgroup) edge (Submodule);
    \end{tikzpicture}
  }
  \centering
  \label{alg-heirarchy: F}
\end{figure}

@@

@@

\begin{minted}{coq}
  Definition finitely_generated {n: nat}(genSet: t M n) :=
    forall (elt: M),
      exists (coeffs: t R n),
        elt =M= linear_combin coeffs genSet.
\end{minted}

@@

@@

Even if it were possible not to overwhelm a system with
these infinitely many calls to a single proof tactic, one would still have to
invoke more tactics to finish the proof with an application of Zorn's lemma,
which finally guarantees us a maximal ideal containing \(x\). To summarize, we
are forced to run the following proof script which will never get past calling
\mintinline{coq}{generate_larger_ideal} infinitely many times.
\begin{minted}{coq}
  (* must be called infinitely often *)
  repeat generate_larger_ideal.
  (* called after the above non-terminating call finishes *)
  zorns_lemma.
\end{minted}

@@

\begin{minted}{coq}
Axiom comm_ring_nonunit_maximal_ideal:
  forall (x: Carrier),
    ~ is_unit equiv mul one x ->
    exists (P: Carrier -> Prop)
      (P_proper: Proper (equiv ==> iff) P)
    	(P_ideal: Ideal add zero minus mul P),
      P x /\ maximal_ideal P.
\end{minted}

@@

\begin{minted}{coq}
Context {P_ideal: Ideal Radd Rzero Rminus Rmul P}.
Context {P_maxideal: maximal_ideal Requiv Radd ... Rmul P}.
Context {R_local: local_ring Requiv Radd Rzero Rminus Rmul}.

@@

\begin{minted}{coq}
Lemma module_fin_gen_ideal_module:
  forall {n: nat}(genSet: t M n),
    finitely_generated Mequiv Madd Mzero action genSet ->
    forall {m: nat}(coeffs: t R m)(elts: t M m),
      Forall P coeffs ->
      exists (coeffs': t R n),
        linear_combin Madd Mzero action coeffs elts =M=
          linear_combin Madd Mzero action coeffs' genSet /\
        Forall P coeffs'.
\end{minted}

This lemma's proof follows from a straightforward argument based on definitions, by
induction on the number of elements in a fixed generating set for $M$, which we
informally describe: By definition, $x \in I M$ can  be written, for some
positive integer $k$ and elements $r_i \in R$ and $w_i \in M$,
$1 \leq i \leq k$, as $x = r_1 \cdot w_1 + r_2 \cdot w_2 + \cdots +
r_k \cdot w_k$. What's more, by definition of a finite generating set $u_{1},
\dots, u_{n}$ for $M$, each $w_i$ equals $c_{i1} \cdot u_1 + c_{i2} \cdot u_2 +
\cdots + c_{in} \cdot u_n$ for appropriate choices of $c_{ij} \in R$. Hence,
inductively applying associativity, 
\begin{align*}
  x & = \sum_{i=1}^{k} r_i \cdot w_i
    = \sum_{i=1}^{k} r_i \cdot \left(\sum_{j=1}^n c_{ij} \cdot  u_j\right) \\
    & = \sum_{j=1}^{n}\sum_{i=1}^{k} r_i \cdot (c_{ij} \cdot u_j) 
    = \sum_{j=1}^{n}\left(\sum_{i=1}^{k} c_{ij} \cdot r_i\right) \cdot u_j.   
\end{align*}
By the absorption property of ideals, each  $c_{ij}  \cdot r_i$ is in $I$, and since ideals
are closed under addition, we inductively conclude that the coefficient $a_j
:= c_{1j} \cdot  r_1 +  c_{2j} \cdot  r_2 +  \cdots c_{kj}\cdot r_k$ of $u_j$
is also in $I$.

@@

In Coq, we work backward to establish \eqref{equation1: e}. The comment following
each tactic appearing in the code below offers a brief indication of its effects on the goal.
\begin{minted}[linenos,firstnumber=157,stepnumber=5]{coq}
  (* (1 - a1) u1 = ... *)
  assert ((Rone [+] Rminus a1) <.> u1 =M=
    linear_combin Madd Mzero action coeffs' generatingSet').
  { (* 1 u1 + (-a1) u1 = ... *)
    setoid_rewrite (module_distrib_Radd Radd Rmul Rone
      Mequiv Madd Mzero Mminus action).
    (* u1 + (-a1) u1 = ... *)
    setoid_rewrite (module_Rone Radd Rmul Rone
      Mequiv Madd Mzero Mminus action).
    (* u1 - a1 u1 = ... *)
    setoid_rewrite (module_minus_l Requiv Radd ... Rone
      Mequiv Madd Mzero Mminus action).
    symmetry. (* ... = u1 - a1 u1 *)
    (* ... + a1 u1 = u1 *)
    apply (group_move_r Mequiv Madd Mzero Mminus).
    (* u1 = ... + a1 u1 *)
    symmetry.
    assumption. }
\end{minted}

Since a proper ideal contains no units and $a_1$ is taken to be in
$\mathfrak{m}$, it is not a unit. Hence, by the formalized statement mentioned
early in \Cref{formal-proof: S}, $1 - a_{1}$ is a unit of $R$. Let $b_{1} \in R$ denote its 
multiplicative inverse, so that $b_1 \cdot  (1 - a_{1}) = 1$. Multiplying this
element on the either side of \eqref{equation1: e}, we deduce the following.  
\begin{align}
\label{simplify-line-1}
b_1 \cdot \left((1 - a_{1}) \cdot u_{1} \right)
  & = b_1 \cdot (a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1}) \\ 
\label{simplify-line-2}
\left( b_1 \cdot (1 - a_{1})\right) \cdot u_{1}
  & = b_1 \cdot (a_{2} \cdot u_{2}) + \cdots + b_1 \cdot (a_{n+1} \cdot u_{n+1}) \\ 
   \label{simplify-line-3}
u_1 = 1 \cdot u_{1}
  & = (b_1 \cdot  a_{2}) \cdot u_{2} + \cdots + (b_1  \cdot  a_{n+1}) \cdot u_{n+1} 
\end{align}
\begin{minted}[linenos,firstnumber=181,stepnumber=5]{coq}
  pose proof
    (local_comm_ring_sub_1_nonunit Requiv Radd ... Rone
      R_local x1 Hx1_nonunit) as H1ma1_unit.
  (* Getting to u1 = (b1 coeffs') . genSet *)
  (* 1 - a1 is a unit *)
  inversion_clear H1ma1_unit as [b1 Hb1].
  (* b1 (1 - a1) = 1 *)
  setoid_rewrite (commutative Requiv Rmul) in Hb1.
\end{minted}

This block of code has the effect of naming \(b_{1}\) as the inverse of the
unit \(1 - a_{1}\), and storing in the hypothesis \texttt{Hb1} the equation
\(b_{1} \cdot (1 - a_{1}) = 1\). The remainder of the code goes on to multiply on the
left by \(b_{1}\) in the equation \texttt{H} in order to establish  \eqref{simplify-line-1}.
Going on and applying the axioms of a module over a commutative ring, along with hypothesis \texttt{Hb1}, we can
simplify the left hand side of \texttt{H} to be just \(u_{1}\), as in \eqref{simplify-line-3}.
\begin{minted}[linenos,firstnumber=last,stepnumber=5]{coq}
  apply (module_op_l Requiv Mequiv action) with (r:=b1) in H.
  (* H: (b1 (1 - a1)) u1 = ... *)
  setoid_rewrite <- (module_distrib_Rmul Radd Rmul Rone
    Mequiv Madd Mzero Mminus action) in H.
  (* H: (1) u1 = ... *)
  setoid_rewrite Hb1 in H.
  (* H: u1 = ... *)
  setoid_rewrite (module_Rone Radd Rmul Rone
    Mequiv Madd Mzero Mminus action) in H.
\end{minted}
In particular, the generator $u_1$ can be written as a scalar combination of
the $n$ generators $u_2, \ldots, u_{n+1}$, and is superfluous. Hence $M$ can be
generated by $n$ elements, and $M=0$ by the inductive hypothesis. 
Though showing that the inductive hypothesis holds is more technical in Coq than in this
informal proof, the extra steps are essentially bookkeeping.

@@

\backmatter
\bmhead{Acknowledgments}
This work is funded in part by the NSA Science of Security initiative contract
\#H98230-18-D-0009 and Defense Advanced Research Project Agency contract
\#HR0011-18-9-0001 and Honeywell FMT Purchase Order \#N000422909. The views and
conclusions contained in this document are those of the authors and should not
be interpreted as representing the official policies, either expressed or
implied, of the United States Government.

Witt acknowledges support from NSF CAREER Award DMS-1945611, the Keeler
Intra-University Professorship from the University of Kansas, and the Ruth I.\,
Michler Memorial Prize from the Association for Women in Mathematics.
\bibliography{references}
\end{document}
